Succinct representations for abstract interpretation

### 2011-11-01 papers/PLDI2012/implicitization.tex
reponse a une question

We experimented with a heuristic
of dynamic construction of the $\sigma_i$ functions, adapted from
\citet{DBLP:conf/pldi/GulwaniZ10}. 
\DM{Cette heuristique, je croyais que c'était nous qui l'avions trouvée,
et qu'elle n'était pas dans Gulwani?}
\JH{Non. Gulwani fait la même chose en un peu plus complique (voir commentaire
suivant)}
\MM{Du coup, la contribution~\ref{contr:disjunctive} devrait être
  affaiblie un peu je suppose. Gulwani fait aussi du SMT-solving ?}
We start with one single
disjunct per control point ($m_i=1$ for each $i, p_i \in P_R$) 
and empty maps $\sigma_i$.
$M$ denotes an upper bound on the number of disjuncts per control point.
$\sigma_i(j,k)$ is then constructed on the fly only when needed.
When $\sigma_i(j,k)$ needs to be computed, we first compute the image of the
abstract value $X_{i,j}$ by the path indexed by $k$, and try to find an existing
disjunct of index $j'$ so that the least upper bound of the two abstract values is exactly their union (this can be tested using SMT-solving).
If such an index exists, then we set $\sigma_i(j,k) = j'$.
Otherwise:
\begin{itemize}[itemsep=-1\parsep,topsep=0pt]
	\item if $m_i < M$, we increase $m_i$ by $1$ and define $\sigma_i(j,k) = m_i$
	\item if $m_i = M$, we define $\sigma_i(j,k) = M$ 
		\JH{A la place, Gulwani cherche l'invariant qui a le plus de contraintes
		d'egalite en commun pour definir son $sigma$. Nous, on le met dans M, pour simplifier}
\end{itemize}

>>>>

We experimented with a heuristic
of dynamic construction of the $\sigma_i$ functions, adapted from
\citet{DBLP:conf/pldi/GulwaniZ10}. 
\DM{Cette heuristique, je croyais que c'était nous qui l'avions trouvée,
et qu'elle n'était pas dans Gulwani?}
\JH{Non. Gulwani fait la même chose en un peu plus complique (voir commentaire
suivant)}
\MM{Du coup, la contribution~\ref{contr:disjunctive} devrait être
  affaiblie un peu je suppose. Gulwani fait aussi du SMT-solving ?}
\DM{Non, Gulwani énumère tous les chemins un par un à tous les coups.}
We start with one single
disjunct per control point ($m_i=1$ for each $i, p_i \in P_R$) 
and empty maps $\sigma_i$.
$M$ denotes an upper bound on the number of disjuncts per control point.
$\sigma_i(j,k)$ is then constructed on the fly only when needed.
When $\sigma_i(j,k)$ needs to be computed, we first compute the image of the
abstract value $X_{i,j}$ by the path indexed by $k$, and try to find an existing
disjunct of index $j'$ so that the least upper bound of the two abstract values is exactly their union (this can be tested using SMT-solving).
If such an index exists, then we set $\sigma_i(j,k) = j'$.
Otherwise:
\begin{itemize}[itemsep=-1\parsep,topsep=0pt]
	\item if $m_i < M$, we increase $m_i$ by $1$ and define $\sigma_i(j,k) = m_i$
	\item if $m_i = M$, we define $\sigma_i(j,k) = M$ 
		\JH{A la place, Gulwani cherche l'invariant qui a le plus de contraintes
		d'egalite en commun pour definir son $sigma$. Nous, on le met dans M, pour simplifier}
\end{itemize}
